Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2019-03-28 Paper/Figures.Rnw
Onset/offset plot improvements

    monthBarY = 0.7 + (0.5 - 5.5) * 0.04
    monthGrob = function(month) {
        textGrob(epiWeekLabels[month], just="right", gp=gpar(fontsize="6.4", col="grey30"))
    }

    plot = ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_errorbarh(aes(xmin=lower, xmax=upper, y=county), height=.1) + 
        geom_point(aes(x=median, y=county), size=.75) + 
        geom_blank(data=limits, aes(x=min)) + 
        geom_blank(data=limits, aes(x=max)) + 
        labs(aes(y=variable)) +
        facet_wrap(~variable, ncol=2, scales="free_x", labeller=onsetOffsetLabeller) +
        scale_y_discrete(labels=countyLabels, limits=rev(unique(data$county))) + 
        scale_x_continuous(breaks=seq(0, 52, 2), minor_breaks=seq(1, 52)) + 
        labs(x=NULL) + 
        annotation_custom(monthGrob(4), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[4], xmax=monthBoundaries$mid[4]) + 
        annotation_custom(monthGrob(5), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[5], xmax=monthBoundaries$mid[5]) + 
        annotation_custom(monthGrob(9), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[9], xmax=monthBoundaries$mid[9]) + 
        annotation_custom(monthGrob(10), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[10], xmax=monthBoundaries$mid[10]) + 
        theme(
            panel.grid.major.x=element_line(size=rel(2)),
            panel.grid.minor.x=element_line(size=rel(2)),
            panel.grid.major.y=element_blank(),
            axis.title.y=element_blank(),
            axis.ticks.y=element_blank(),
            axis.text.y=element_text(hjust=1)
        )

	  plotGrob = ggplotGrob(plot)
	  plotGrob$layout$clip[grepl("panel", plotGrob$layout$name)] <- "off"
	  grid.draw(plotGrob)

@@

    monthBarY = 1998.5 + (1998.5 - 2013.5) * 0.04

    plot = ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_errorbarh(aes(xmin=lower, xmax=upper, y=epiyear), height=.3) + 
        geom_point(aes(x=median, y=epiyear), size=.75) +
        geom_blank(data=limits, aes(x=min)) + 
        geom_blank(data=limits, aes(x=max)) + 
        facet_wrap(~variable, ncol=2, scales="free_x", labeller=onsetOffsetLabeller) +
        scale_y_continuous(breaks=seq(1990, 2020, by=5)) +
        scale_x_continuous(breaks=seq(0, 52, 2), minor_breaks=seq(1, 52)) + 
        annotation_custom(monthGrob(4), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[4], xmax=monthBoundaries$mid[4]) + 
        annotation_custom(monthGrob(5), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[5], xmax=monthBoundaries$mid[5]) + 
        annotation_custom(monthGrob(9), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[9], xmax=monthBoundaries$mid[9]) + 
        annotation_custom(monthGrob(10), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[10], xmax=monthBoundaries$mid[10]) + 
        labs(x=NULL) + 
        theme(
            panel.grid.major.x=element_blank(),
            panel.grid.minor.x=element_line(size=rel(2)),
            axis.title.y=element_blank()
        )

  	plotGrob = ggplotGrob(plot)
  	plotGrob$layout$clip[grepl("panel", plotGrob$layout$name)] <- "off"
  	grid.draw(plotGrob)

>>>>

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_errorbarh(aes(xmin=lower, xmax=upper, y=county), height=.1) + 
        geom_point(aes(x=median, y=county), size=.75) + 
        geom_blank(data=limits, aes(x=min)) + 
        geom_blank(data=limits, aes(x=max)) + 
        labs(aes(y=variable)) +
        facet_wrap(~variable, ncol=2, scales="free_x", labeller=onsetOffsetLabeller) +
        scale_y_discrete(labels=countyLabels, limits=rev(unique(data$county))) + 
        scale_x_continuous(breaks=seq(0, 52, 2), minor_breaks=seq(1, 52)) + 
        labs(x=NULL) + 
        geom_rect(data=onsetOffsetMonthBoundaries, aes(xmin=min + 0.05, xmax=max - 0.05, ymin=0.6, ymax=0.8), color="grey70", fill="grey70") + 
        geom_text(data=onsetOffsetMonthBoundaries, aes(x=mid, label=label, y=0.7), color="white", size=2.2) + 
        theme(
            panel.grid.major.x=element_line(size=rel(2)),
            panel.grid.minor.x=element_line(size=rel(2)),
            panel.grid.major.y=element_blank(),
            axis.title.y=element_blank(),
            axis.ticks.y=element_blank(),
            axis.text.y=element_text(hjust=1)
        )

@@

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_errorbarh(aes(xmin=lower, xmax=upper, y=epiyear), height=.3) + 
        geom_point(aes(x=median, y=epiyear), size=.75) +
        geom_blank(data=limits, aes(x=min)) + 
        geom_blank(data=limits, aes(x=max)) + 
        geom_rect(data=onsetOffsetMonthBoundaries, aes(xmin=min + 0.05, xmax=max - 0.05, ymin=1997.8, ymax=1998.2), color="grey70", fill="grey70") + 
        geom_text(data=onsetOffsetMonthBoundaries, aes(x=mid, label=label, y=1998), color="white", size=2.2) + 
        facet_wrap(~variable, ncol=2, scales="free_x", labeller=onsetOffsetLabeller) +
        scale_y_continuous(breaks=seq(1990, 2020, by=5)) +
        scale_x_continuous(breaks=seq(0, 52, 2), minor_breaks=seq(1, 52)) + 
        labs(x=NULL) + 
        theme(
            panel.grid.major.x=element_blank(),
            panel.grid.minor.x=element_line(size=rel(2)),
            axis.title.y=element_blank()
        )
